Contention Management for 5G

### 2017-02-14 article/article.tex
retouche star topology without waiting time

  \subsection{MIN-PRA}
    Exemple de cas polynomiaux

\section{The Star Topolgy}

  \subsection{Intro}
    PALL NP-Hard car PRA NP-Hard\\

      In this section, we consider a particular case of the model, in which for each $(u,v)$ , the route is the same in both directions. This means that $\forall (u,v) \in {\cal C}, {\cal R}_{\cal C}(u,v)$ uses the same arcs as ${\cal R}_{\cal C}(v,u)$ in the opposite direction.\\
      Furthermore, the following algorithms and results were designed for a particular topology of network, in which all the routes uses a same common switch.
        \begin{center}
	  \includegraphics[scale=0.8]{Fig4.pdf}
	\end{center}
      Let us call {\bf LN} (leaves node) the central node connected to leaves, and {\bf SN} (sources node), the one connected to sources. The period in those nodes are respectively called {\em forward period}, and {\em backward period}.
      The weight on the link between the two central nodes is simplified in the forthcoming calculations.

  \subsection{No waiting times}
    \subsubsection{Shortest-longest}
      \paragraph{Algo}
      \paragraph{Period}
    \subsubsection{Greedy Algorithm with higher bound}

	\begin{algorithm}[H]
	\caption{Greedy with Higher bound Period(GHP)}
	\begin{algorithmic}
	\REQUIRE ${\cal R}_{\cal C}$, period $P$
	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
	\STATE $P1[P]$ slots of size $\tau$ in first way period.
	\STATE $P2[P]$ slots  of size $\tau$ in back way period.
	\FORALL{route i in ${\cal R}_{\cal C}$ }

>>>>

  \subsection{Tractable cases of PRA}

    In this section, we present a few polynomial cases, in particular when the conflict depth is one.

    The problem PALL seems to be hard to solve, even for very simple classes of graphs, as seen in the next section.

\section{The Star Topology}

      In this section, we consider graphs with a very simple topology that we call the {\bf star topology}. 
      First, for each arc $(u,v)$, there is also an arc $(v,u)$ with the same weight.
      Moreover, there is a special arc, the central arc, which is shared by all routes.
      All routes consist from an arc from its source to the source node, denoted by {\bf SN},
      then the central arc to {\bf TN}, the target node, and an arc to its target. In addition to SN and TN,
      there are two sets $S$ and $T$ of cardinality $n$ and ${\cal C}$ a symmetric assignment from $S$ to $T$. 
      The routes are the directed paths of the form $s_i,SN,TN,t_i$ and $t_i,TN,SN,s_i$.

       \begin{center}
	  \includegraphics[scale=0.8]{Fig4.pdf}
	\end{center}

      We assume the weight of the central arc to be $0$ since it appears in every route,
      its value does not matter when considering affectations. Collisions between messages can 
      only appear at node SN on the way forward and at node TN on the way back. 
  \todo{Définir la forward period et la backward period et dire à quoi correspond une affectation en terme de forward et backward period (placement de messages dans la première période}     
%       Therefore, 
%       finding an $(P,\tau)$-periodic affectation without collision, is equivalent to fix ...

%       
%       between the two central nodes is simplified in the forthcoming calculations.
%       Let us call {\bf SN} (source node) the central node connected to leaves, and {\bf SN} (sources node), the one connected to sources. The period in those nodes are respectively called {\em forward period}, and {\em backward period}.

  \subsection{Solving PALL without waiting times}

  In this subsection, we deal with a simpler version of the problem PALL.
  We ask for a $(P,\tau)$-periodic affectation with all waiting times equal to $0$. 
  In that case $T_{max}$ is not relevant anymore. Since $w_i=0$, choosing $m_i$, the offset of the route from
  $s_i$ to $t_i$, also sets the offset of the route from $t_i$ to $s_i$ to $m_i + t(r_i)$.
  Moreover, in this context the weight of the arcs from $s_i$ to SN have no impact, therefore we assume they are 
  equal to $0$.

    \subsubsection{Shortest-longest policy}

    We present a simple policy, which works when the period is large with regards to the delay of the routes.
    We send the messages in order from the shortest route to the longest route. 
    \todo{Preuve en deux lignes que ça ne collisionne pas à condition que la période soit assez grande}

      \paragraph{Algo}
      \paragraph{Period}

    \subsubsection{Greedy Algorithm}

    We introduce a greedy algorithm to build a $(P,\tau)$-periodic affectation, which provably works when
    the period is large enough with regards to the number of routes and size of messages. In other words, 
    we can always find a solution when the network is far from saturated.

    \begin{proposition}
    There is an algorithm, which finds a $(P,\tau)$-periodic affectation in time $O(n^2)$ when $P \geq 3n\tau$.
    \end{proposition}
    \begin{proof}
     We consider the time period at the vertex SN and cut it into consecutive macro slots of time of size $\tau$. The algorithm works in the following way: select the first route for which the offset as not been chosen. Try every offset which put the message in a  
     free macro slot in the period at SN. It also fixes the position of a message a TN, and we choose the first offset which does not create a collision at TN. 
     Assume we choose the offset of the route $r_{k+1}$, we have  at least $3n - k$ free macro-slots, since $P \geq 3n\tau$. Each of these $3n - k$ possible offset values translates into $3n - k$ positions of messages in the period at TN. All these positions are separated by at least $\tau$ slots. There are already $k$ messages of size $\tau$ in the period at TN. One such message can intersect at most $2k$ potential positions, therefore  amongst the possible $3n - k$ positions, there are  $3n - k -2k$ which are without collision. Since $k < n$, one of the choice is without collision, which proves that the algorithm terminates and find a
     $(P,\tau)$-periodic affectation. To ensure a complexity linear in $n$, it is enough to maintain a list of the free slices at SN and a list of the free intervals at TN. 
    \end{proof}

    \todo{Avec une structure de données plus maligne on doit pouvoir faire n, non ?}

	\begin{algorithm}[H]
	\caption{Greedy affectation}
	\begin{algorithmic}
	\REQUIRE ${\cal R}_{\cal C}$, period $P$
	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
	\STATE $P1[P]$ slots of size $\tau$ in first way period.
	\STATE $P2[P]$ slots  of size $\tau$ in back way period.
	\FORALL{route i in ${\cal R}_{\cal C}$ }
